---
title: "2019 Librarian Survey Report"
author: "UP School of Library and Information Studies"
date: "`r Sys.Date()`"
output:
  word_document:
    fig_width: 8
    toc: yes
  pdf_document:
    toc: yes
---
\newpage

# About This Report

The **University of the Philippines School of Library and Information Studies (UPSLIS)** conducted a study of Philippine Librarians from November 2018 to October 2019. This endeavor was the first-ever wide-scale study undertaken to collect the occupational profile of Librarians in the Philippines. The study was motivated by the fact that we do not have any baseline data about Philippine Librarians. While we may assume that more women practice librarianship in the Philippines than males, we do not have empirical data to support such a claim. UPSLIS hopes that this report, together with the raw dataset and manual on how to process and analyze the dataset, will:

-	Gain a deeper insight into the current state of librarians in the Philippines
-	Enable other researchers to validate and extend this current project to create more follow-up and comprehensive studies
-	Serve as a benchmarking tool for future LIS research
-	Create opportunities for collaboration with other researchers not only in the LIS field but with other disciplines as well
-	Assist policymakers and decision-makers in drafting and creating policies and guidelines that would affect the LIS profession in the Philippines.

UPSLIS also endeavors to conduct another census in five to six years to provide a complete longitudinal picture of the changes and development in the profession.

# Background
In 2015, UPSLIS conducted a study to determine the status of archives and records management practitioners in the Philippines. The survey was funded by the National Committee on Archives of the National Commission for Culture and the Arts. The data gathered served as the first comprehensive data of archives and records managers concerning their education, work, and prospects, similar to what this study endeavored to accomplish. The findings became the basis for subsequent training programs for records managers and archivists. The UPSLIS endeavored to conduct the same for librarians with the said accomplishment. 

In 2017, Taban developed a tool for occupational profiling specific to librarians through her undergraduate thesis Occupational Census Profiling Tool for Librarians in the Philippines. This research serves as the tool for this study. Taban's research was guided by Labaw's framework in the formulation of questionnaire design. Labaw posits that the basic principle is for the respondents to define which questions, words, and concepts, among others, can be included. This framework indicates that several pre-tests should be conducted to determine a suitable questionnaire design. With three sets of questionnaires tested among several respondents, the study determined the appropriate ordering of questions, categorization of questions, suitable options or responses, and the like. The third cycle or the third run of the questionnaire was the most appropriate set of questions used in this project.

# Methodology

The study adopted an exploratory, descriptive approach to provide a snapshot of an occupational baseline profile of Filipino Librarians. The project proponents aimed to highlight patterns, outliers, and other observations through the summarization and visualization of the data.

## Instrument

The questionnaire was developed in 2017 through Taban's thesis. Its goal was to determine the minimum set of questions that would comprise an occupational census questionnaire for librarians. She subsequently tested three questionnaires among several respondents, for which she made revisions based on determining issues and concerns. This study is the first wide-scale survey using the tool, and it may still be revised for improvement. The online tool also has its pros and cons. While it may be convenient distribution, it can also be limited to only those with internet access and digital technologies. We can also interpret outliers as possible incorrect input due to the respondents' unfamiliarity with the tool.

## Data Gathering

The researchers opted to use Mentimeter to provide a real-time visualization report of the data gathered. Also, as presented at a conference, it was hoped that a quick view of the data could be delivered after the participants responded. However, due to lack of time, the questionnaire was only introduced during the 2018 PLAI Congress along with the link. The researchers also posted the survey link in the official Facebook group of the different PLAI regional councils to collect responses from librarians who were not present during the PLAI Congress 2018. A total of 684 responses were recorded that can be used in making statistical inferences with a 4% margin of error.

## Data Cleaning and Preparation

Data collected using Mentimeter were exported via CSV. Upon inspection, the dataset produces a data frame with 685 rows of individual data and 67 variables.

```{r Preview, warning=FALSE, include=FALSE}
library(tidyverse)
```

```{r Colnames, echo=FALSE, warning=FALSE}
colnames(read_csv("librariancensus.csv"))
```

Rows that only contained timestamp data were deleted as these represents individuals who tried to answer the census but never push through answering majority of the questions. Most of the variables were summarized by creating a bar graph. Numerical variables were summarized by:

- defining a class interval and creating a bar graph
- through a histogram
- through overlapping a boxplot, violinplot, and dotplot

Statiscal measures were reported unfiltered but the visualizations have the outliers trimmed so that the graphs will not be skewed. Refer to the Codebook on how the numerical variables were trimmed.

For open-ended questions, the researchers use a text-mining approach to analyze the general sentiment of the respondents. Word count and proximity measures were used to generate a dendrogram.

The researchers also created additional variables to ease the process of summarizing the data. For example, a variable `age_group` was created to convert the numerical nature of librarians age to the following categories:

- 21 to 30
- 31 to 40
- 41 to 50
- 51 to 60
- Greater than 60

The data were processed using:

- RStudio 2022.02.3+492 "Prairie Trillium" Release (1db809b8323ba0a87c148d16eb84efe39a8e7785, 2022-05-20) for Windows
- R-4.2.1 language
- tidyverse package version 1.3.2
- tm package version:	0.7-8

```{r Ingress, include=FALSE}
# Load needed package
library(tidyverse)
library(tm)

#Load the raw "librariancensus.csv" dataset
dataset <- read_rds("librariancensus.rds")

#controls how many digits will be printed
options(digits=4) 

#Initialize a pseudorandom number generator to obtain the same output during simulation
set.seed(12)
```

# Summary of responses

## Question: Are you currently a licensed librarian (R.A. 9246) ?

-   Yes, I have a valid and up-to-date PRC license for librarians
-   No, I have not renewed my license
-   No, I have never taken any licensure examination for librarians and/or never applied for a PRC license for librarians

```{r PRC License, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(licensed)) %>%
ggplot(aes(x = licensed, fill = licensed)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: PRC License", "n=659") + guides(fill = "none") + scale_fill_viridis_d()
```

## Question: Are you currently residing in the Philippines?

-   Yes, I am currently residing and staying in the Philippines
-   No, I am in the Philippines right now but only for vacation
-   No, I am currently residing outside the Philippines

```{r Residency, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(philippines)) %>%
ggplot(aes(x = philippines, fill = philippines)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Residency", "n=657") + guides(fill = "none") + scale_fill_viridis_d()
```

## Question: Kindly indicate which gender you identify the most

-   Man
-   Woman
-   LGBTQ+
-   Prefer not to say

```{r Gender, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(gender)) %>%
ggplot(aes(x = gender, fill = gender)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Gender", "n=659") + guides(fill = "none") + scale_fill_viridis_d()
```

## Question: Kindly indicate your age

```{r Summary Age, echo=FALSE}
# Inspect the responses
summary(dataset$age)
```

```{r Age, echo=FALSE}
dataset %>%
filter(!is.na(age_group)) %>%
ggplot(aes(x = age_group, fill = age_group)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Age", "n=655") + guides(fill = "none") + scale_fill_viridis_d()
```

```{r Histogram Age, echo=FALSE, warning=FALSE}
dataset %>%
filter(!is.na(age)) %>%
filter(age > 20) %>%
filter(age < 65) %>%
ggplot(aes(x = age, fill = age)) + geom_histogram(bins = 8) + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Age", "n=646") + guides(fill = "none") + scale_fill_viridis_d()
```

```{r Boxplot Age, echo=FALSE}
# Graph the data: boxplot + violin plot + dot plot
dataset %>%
filter(!is.na(age)) %>%
filter(age > 20) %>%
filter(age < 65) %>%
ggplot(aes(x = 1, y = age)) + geom_violin(adjust=.7) + geom_boxplot(width = .1, fill = "black") + geom_dotplot(aes(y = age), binaxis = "y", binwidth = .3, stackdir = "center", alpha = .5) + stat_summary(fun = mean, geom = "point", fill = "white", shape = 21, size = 2.5) + coord_flip() + theme(axis.text.y = element_blank()) + xlab("Distribution") + ylab("Age") + ggtitle("Distribution of Responses: Age(Boxplot)", "n=646")
```

## Question: Are you currently employed and/or working?

-   Yes, I am currently employed by an institution, agency, individual or similar.
-   Yes, I am currently self-employed and/or doing freelance and consultancy work.
-   No, I am currently not working for reasons other than retirement.
-   No, I am a retiree.

```{r Currently Working, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(working)) %>%
ggplot(aes(x = working, fill = working)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Currently Working", "n=657") + guides(fill = "none") + scale_fill_viridis_d()
```

## Question: Kindly indicate the setting, field or industry you are primarily working in

-   library
-   archives and/or records management
-   academic institution (non-librarian position)
-   information technology, computer science, software / database engineering and other similar line of work
-   museum and heritage work
-   social services

```{r Industry, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(industry)) %>%
ggplot(aes(x = industry, fill = industry)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Industry", "n=651") + guides(fill = "none") + scale_fill_viridis_d()
```

## Question: How long have you been working as a professional after passing the licensure exam for librarians (cumulative years)

```{r Summary Years of Service, echo=FALSE}
# Inspect the responses
summary(dataset$years_service)
```

```{r Years of Service, echo=FALSE}
# Graph the data: bar graph
dataset %>%
filter(!is.na(years_service_group)) %>%
ggplot(aes(x = years_service_group, fill = years_service_group)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Years of Service", "n=648") + guides(fill = "none") + scale_fill_viridis_d()
```

```{r Histogram Years of Service, echo=FALSE}
# Graph the data: histogram
dataset %>%
filter(!is.na(years_service)) %>%
filter(years_service < 35) %>%
ggplot(aes(x = years_service, fill = years_service)) + geom_histogram(bins = 8) + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Years of Service", "n=648") + guides(fill = "none") + scale_fill_viridis_d()
```

```{r Boxplot Years of Service, echo=FALSE}
# Graph the data: boxplot + violin plot + dot plot
dataset %>%
filter(!is.na(years_service)) %>%
filter(years_service < 35) %>%
ggplot(aes(x = 1, y = years_service)) + geom_violin(adjust=.8) + geom_boxplot(width = .1, fill = "black") + geom_dotplot(aes(y = years_service), binaxis = "y", binwidth = .13, stackdir = "center", alpha = .5) + stat_summary(fun = mean, geom = "point", fill = "white", shape = 21, size = 2.5) + coord_flip() + theme(axis.text.y = element_blank()) + xlab("Distribution") + ylab("Years of Service") + ggtitle("Distribution of Responses: Years of Service(Boxplot)", "n=648")
```

## Question: Kindly indicate the type of institution (in terms of ownership) you are primarily working in

-   government
-   private (in-house)
-   private (BPO)
-   non-profit

```{r Institution, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(institution)) %>%
ggplot(aes(x = institution, fill = institution)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Institution", "n=643") + guides(fill = "none") + scale_fill_viridis_d()
```

## Question: Kindly indicate your current tenure status

-   permanent
-   contractual
-   voluntary work
-   job order (J.O.)
-   self-employed, freelancing or working with multiple institutions

```{r Tenure, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(tenure)) %>%
ggplot(aes(x = tenure, fill = tenure)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Tenure", "n=639") + guides(fill = "none") + scale_fill_viridis_d()
```

## Question: Kindly indicate your current monthly gross salary or income range (before deductions)

```{r Summary Gross Salary, echo=FALSE}
# Inspect the responses
summary(dataset$gross_salary)
```


```{r Gross Salary, echo=FALSE}
# Graph the data: bar graph
dataset %>% 
filter(!is.na(gross_salary_group)) %>%
ggplot(aes(x = gross_salary_group, fill = gross_salary_group)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Gross Salary", "n=562") + guides(fill = "none") + scale_fill_viridis_d()
```

```{r Histogram Gross Salary, echo=FALSE}
# Graph the data: histogram
dataset %>%
filter(!is.na(gross_salary)) %>%
filter(gross_salary > 10) %>%
filter(gross_salary < 65) %>%
ggplot(aes(x = gross_salary, fill = gross_salary)) + geom_histogram(bins = 10) + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Gross Salary", "n=508") + guides(fill = "none") + scale_fill_viridis_d()
```

```{r Boxplot Gross Salary, echo=FALSE}
# Graph the data: boxplot + violin plot + dot plot
dataset %>%
filter(!is.na(gross_salary)) %>%
filter(gross_salary > 10) %>%
filter(gross_salary < 65) %>%
ggplot(aes(x = 1, y = gross_salary)) + geom_violin(adjust=2) + geom_boxplot(width = .1, fill = "black") + geom_dotplot(aes(y = gross_salary), binaxis = "y", binwidth = .3, stackdir = "center", alpha = .5) + stat_summary(fun = mean, geom = "point", fill = "white", shape = 21, size = 2.5) + coord_flip() + theme(axis.text.y = element_blank()) + xlab("Distribution") + ylab("Gross Salary") + ggtitle("Distribution of Responses: Gross Salary(Boxplot)", "n=508")
```

## Kindly indicate your current monthly net salary or income range (after deductions)

```{r Summary Net Salary, echo=FALSE}
# Inspect the responses
summary(dataset$net_salary)
```


```{r Net Salary, echo=FALSE}
# Graph the data: bar graph
dataset %>%
filter(!is.na(net_salary_group)) %>%
ggplot(aes(x = net_salary_group, fill = net_salary_group)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Net Salary", "n=550") + guides(fill = "none") + scale_fill_viridis_d()
```

```{r Histogram Net Salary, echo=FALSE}
# Graph the data: bar graph
dataset %>%
filter(!is.na(net_salary)) %>%
filter(net_salary > 10) %>%
filter(net_salary < 65) %>%
ggplot(aes(x = net_salary, fill = net_salary)) + geom_histogram(bins = 10) + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Net Salary", "n=446") + guides(fill = "none") + scale_fill_viridis_d()
```

```{r Boxplot Net Salary, echo=FALSE}
# Graph the data: boxplot + violin plot + dot plot
dataset %>%
filter(!is.na(net_salary)) %>%
filter(net_salary > 10) %>%
filter(net_salary < 65) %>%
ggplot(aes(x = 1, y = net_salary)) + geom_violin(adjust=2) + geom_boxplot(width = .1, fill = "black") + geom_dotplot(aes(y = net_salary), binaxis = "y", binwidth = .3, stackdir = "center", alpha = .5) + stat_summary(fun = mean, geom = "point", fill = "white", shape = 21, size = 2.5) + coord_flip() + theme(axis.text.y = element_blank()) + xlab("Distribution") + ylab("Net Salary") + ggtitle("Distribution of Responses: Net Salary(Boxplot)", "n=446")
```

## Question: Kindly indicate additional benefits, if any (please check all that apply)

-   free shuttle service
-   night differential pay
-   paid vacation and/or sick leaves
-   health card and/or insurance other than PhilHealth
-   monetary allowances
-   NONE / Not Applicable

```{r Benefits, echo=FALSE}
# Summarize by counting the TRUE values per benefits
dataset %>%
summarise("Shuttle service" = sum(shuttle == TRUE), "Night differential" = sum(night_differential == TRUE), "Paid leaves" = sum(paid_leaves == TRUE), "HMO" = sum(hmo == TRUE), "Allowances" = sum(allowances == TRUE), "No benefits" = sum(no_benefits == TRUE)) %>%
gather() %>%
ggplot(aes(x = key, y = value, fill = key)) + geom_col(position = "dodge") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Benefits", "n=630") + guides(fill = "none") + scale_fill_viridis_d() + theme(axis.text.x = element_text(angle = 90)) +
geom_text(x = 1, y = 254, label = "244", colour = "black", size = 4) + 
geom_text(x = 2, y = 269, label = "259", family = "serif", colour = "black", size = 4) +
geom_text(x = 3, y = 38, label = "28", family = "serif", colour = "black", size = 4) +
geom_text(x = 4, y = 124, label = "114", family = "serif", colour = "black", size = 4) +
geom_text(x = 5, y = 463, label = "453", family = "serif", colour = "black", size = 4) +
geom_text(x = 6, y = 46, label = "36", family = "serif", colour = "black", size = 4)
```

```{r Aggregate Benefits, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(benefits6)) %>%
ggplot(aes(x = benefits6, fill = benefits6)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Benefits", "n=630") + guides(fill = "none") + scale_fill_viridis_d()
```

## Question: Other benefits not mentioned in the previous page

```{r Other Benefits, echo=FALSE}
# Create a clean_corpus function 
clean_corpus <- function(corpus) {
    corpus <- tm_map(corpus, removePunctuation)
    corpus <- tm_map(corpus, removeNumbers)
    corpus <- tm_map(corpus, content_transformer(tolower))
    corpus <- tm_map(corpus, removeWords, c(stopwords("en")))
    corpus <- tm_map(corpus, stripWhitespace)
    return(corpus)
}
# Create a text dataset
benefits.text <- paste(dataset$otherbenefits1, dataset$otherbenefits2, dataset$otherbenefits3, dataset$otherbenefits4)
# Create a text corpus
benefit.corpus <- benefits.text %>%
VectorSource() %>%
VCorpus()
# Clean the created corpus
benefit.corpus <- clean_corpus(benefit.corpus)
# Create a dendogram
benefit.corpus %>%
TermDocumentMatrix() %>%
removeSparseTerms(sparse = 0.98) %>%
as.matrix() %>%
dist() %>%
hclust() %>%
plot()
```

## Question: What kind of materials are you currently working with? Kindly check all that applies.

-   hardcopy theses and dissertations
-   hardcopy books / pamphlets / etc
-   electronic material (digital titles, digital archives, etc)
-   law materials and resources
-   archives (physical)
-   data sets
-   institutional files and records
-   NA

```{r Materials, echo=FALSE}
# Summarize by counting the TRUE values per materials
dataset %>%
summarise("These" = sum(theses == TRUE), "Books" = sum(books == TRUE), "Electronic Materials" = sum( electronic_materials == TRUE), "Law Materials" = sum(law_materials == TRUE), "Datasets" = sum(datasets == TRUE), "Archives" = sum(archives == TRUE), "Institutional Materials" = sum(institutional_files == TRUE)) %>%
gather() %>%
ggplot(aes(x = key, y= value, fill = key)) + geom_col(position = "dodge") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Materials", "n=542") + guides(fill = "none") + scale_fill_viridis_d() + theme(axis.text.x = element_text(angle = 90)) +
geom_text(x = 1, y = 298, label = "288", colour = "black", size = 4) + 
geom_text(x = 2, y = 459, label = "449", colour = "black", size = 4) + 
geom_text(x = 3, y = 66, label = "56", colour = "black", size = 4) +
geom_text(x = 4, y = 273, label = "263", colour = "black", size = 4) +
geom_text(x = 5, y = 233, label = "223", colour = "black", size = 4) +
geom_text(x = 6, y = 75, label = "65", colour = "black", size = 4) +
geom_text(x = 7, y = 304, label = "294", colour = "black", size = 4)
```

## Question: Kindly indicate your current work position

-   entry level / junior staff
-   regular / senior staff (non-supervisory)
-   supervisory / mid-management level
-   upper management level / top tier executive
-   consultant / freelancer / self-employed

```{r Position, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(position)) %>%
ggplot(aes(x = position, fill = position)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Position", "n=578") + guides(fill = "none") + scale_fill_viridis_d()
```

## Question: Within the next five (5) years, do you see your self working in the same industry?

-   Yes
-   No (planning to shift to other fields or industry)
-   Maybe / Undecided

```{r 5-year plan, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(fiveyears)) %>%
ggplot(aes(x = fiveyears, fill = fiveyears)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: 5-year plan", "n=585") + guides(fill = "none") + scale_fill_viridis_d()
```

## Question: If your answer was NO or MAYBE in the previous page, indicate the field you wish to pursue

```{r Field to pursue, echo=FALSE}
# Create a clean_corpus function 
clean_corpus <- function(corpus) {
    corpus <- tm_map(corpus, removePunctuation)
    corpus <- tm_map(corpus, removeNumbers)
    corpus <- tm_map(corpus, content_transformer(tolower))
    corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "none", "yes", "like", "library", "librarianship", "want", "work"))
    corpus <- tm_map(corpus, stripWhitespace)
    return(corpus)
}
# Create a text corpus
fiveyearplan.corpus <- dataset$pursue %>%
VectorSource() %>%
VCorpus()
# Clean the created corpus
fiveyearplan.corpus <- clean_corpus(fiveyearplan.corpus)
# Create a dendogram
fiveyearplan.corpus %>%
TermDocumentMatrix() %>%
removeSparseTerms(sparse = 0.995) %>%
as.matrix() %>%
dist() %>%
hclust() %>%
plot()
```

## Question: Kindly indicate your highest educational attainment

-   High School
-   Bachelor's degree (BLIS)
-   Bachelor's degree (non-BLIS)
-   Master's degree (MLIS)
-   Master's degree (non-MLIS)
-   Juris Doctor / Bachelor of Laws
-   Doctor of Philosophy (Ph.D)

```{r Highest Educational Attainment, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(education)) %>%
ggplot(aes(x = education, fill = education)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Highest Educational Attainment", "n=580") + guides(fill = "none") + scale_fill_viridis_d()
```

## Question: Are you currently enrolled in formal studies? (Short Courses, Certificate Program, Diploma Program, Master Program, PhD)

-   Yes
-   No

```{r Currently Enroled, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(enrolled)) %>%
ggplot(aes(x = enrolled, fill = enrolled)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Currently Enroled", "n=579") + guides(fill = "none") + scale_fill_viridis_d()
```

## Question: If your answer was YES, indicate the degree you are currently completing

-   Short \| Certificate \| Diploma Program
-   Bachelor's degree (BLIS)
-   Master's degree (MLIS)
-   Master's degree (non-MLIS)
-   Juris Doctor / Bachelor of Laws
-   Doctor of Philosophy (Ph.D)
-   Post-graduate Certificate or Diploma (LIS)
-   Post-graduate Certificate or Diploma (non-LIS)

```{r Current Enrollment, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(completing)) %>%
ggplot(aes(x = completing, fill = completing)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Current Enrollment", "n=286") + guides(fill = "none") + theme(axis.text.x = element_text(angle = 90)) + scale_fill_viridis_d()
```

## Question: Are you planning to study again in a formal university setting within the next five (5) years?

-   Yes
-   No
-   Maybe

```{r Study Again, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(study_again)) %>%
ggplot(aes(x = study_again, fill = study_again)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Current Enrollment", "n=573") + guides(fill = "none") + scale_fill_viridis_d()
```

## Question: If your answer was YES, kindly provide the degree you wish to study within the next five (5) years

-   Short \| Certificate \| Diploma Program
-   Bachelor's degree (BLIS)
-   Master's degree (MLIS)
-   Master's degree (non-MLIS)
-   Juris Doctor / Bachelor of Laws
-   Doctor of Philosophy (Ph.D)
-   Post-graduate Certificate or Diploma (LIS)
-   Post-graduate Certificate or Diploma (non-LIS)

```{r after5years, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(after5years)) %>%
ggplot(aes(x = after5years, fill = after5years)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Plan within 5 years", "n=430") + guides(fill = "none") + theme(axis.text.x = element_text(angle = 90)) + scale_fill_viridis_d()
```

## Question: Where do you usually acquire your CPD trainings in LIS? Kindly check all that applies

-   within the work place (in-house trainings)
-   government facilitated trainings and symposiums
-   trainings and symposiums facilitated by private entities, individuals and/or corporations
-   NA (Have not attended CPD Trainings yet)

```{r CPD Training, echo=FALSE}
# Summarize by counting the TRUE values per materials
dataset %>%
summarise("in-house trainings" = sum(inhouse == TRUE), "government facilitated" = sum(government == TRUE), "private entities" = sum(private == TRUE), "Have not attended CPD Trainings" = sum(xattended == TRUE)) %>%
gather() %>%
ggplot(aes(x = key, y= value, fill = key)) + geom_col(position = "dodge") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: CPD Training", "n=562") + guides(fill = "none") + scale_fill_viridis_d() + theme(axis.text.x = element_text(angle = 90)) +
geom_text(x = 1, y = 199, label = "189", colour = "black", size = 4) + 
geom_text(x = 2, y = 103, label = "93", colour = "black", size = 4) + 
geom_text(x = 3, y = 168, label = "158", colour = "black", size = 4) +
geom_text(x = 4, y = 434, label = "424", colour = "black", size = 4)
```

## Where do you usually get funding or support for your trainings in LIS?

-   from the work place (private sponsorship)
-   from the government (scholarships, free trainings and seminars, etc)
-   personal funding (personally attended trainings and symposiums and shouldered most of the expenses)
-   NA (Have not attended CPD Trainings yet)

```{r CPD Support, echo=FALSE}
# Summarize by counting the TRUE values per materials
dataset %>%
summarise("personal funding" = sum(support_self == TRUE), "government facilitated" = sum(support_government == TRUE), "private entities" = sum(support_private == TRUE), "Have not attended CPD Trainings" = sum(support_xattended == TRUE)) %>%
gather() %>%
ggplot(aes(x = key, y= value, fill = key)) + geom_col(position = "dodge") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: CPD Support", "n=562") + guides(fill = "none") + scale_fill_viridis_d() + theme(axis.text.x = element_text(angle = 90)) +
geom_text(x = 1, y = 162, label = "152", colour = "black", size = 4) +
geom_text(x = 2, y = 372, label = "362", colour = "black", size = 4) +
geom_text(x = 3, y = 300, label = "290", colour = "black", size = 4) +
geom_text(x = 4, y = 264, label = "254", colour = "black", size = 4)
```

## Question: Are you satisfied with the amount of CPD trainings you have attended for the last two (2) years?

-   Yes, the amount of trainings I received within the last two (2) years is enough.
-   No, the amount of trainings I received within the last two (2) years is not enough.
-   No, the amount of trainings received within the last two (2) years is too much.
-   Maybe
-   NA (Have not attended CPD Trainings yet)

```{r CPD Satisfaction, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(cpdsatisfaction)) %>%
ggplot(aes(x = cpdsatisfaction, fill = cpdsatisfaction)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: CPD Satisfaction", "n=562") + guides(fill = "none") + theme(axis.text.x = element_text(angle = 90)) + scale_fill_viridis_d()
```

## Question: Kindly indicate any challenges you encounter when fulfilling the required CPD trainings

```{r CPD Challenges, echo=FALSE}
# Create a clean_corpus function 
clean_corpus <- function(corpus) {
    corpus <- tm_map(corpus, removePunctuation)
    corpus <- tm_map(corpus, removeNumbers)
    corpus <- tm_map(corpus, content_transformer(tolower))
    corpus <- tm_map(corpus, removeWords, c(stopwords("en")))
    corpus <- tm_map(corpus, stripWhitespace)
    return(corpus)
}
# Create a text dataset
cpdbarriers.text <- paste(dataset$cpdbarriers1, dataset$cpdbarriers2, dataset$cpdbarriers3)
# Create a text corpus
cpdbarriers.corpus <- cpdbarriers.text %>%
VectorSource() %>%
VCorpus()
# Clean the created corpus
cpdbarriers.corpus <- clean_corpus(cpdbarriers.corpus)
# Create a dendogram
cpdbarriers.corpus %>%
TermDocumentMatrix() %>%
removeSparseTerms(sparse = 0.98) %>%
as.matrix() %>%
dist() %>%
hclust() %>%
plot()
```

## Kindly indicate any topics you wish to explore in future trainings

```{r training topics, echo=FALSE}
# Create a clean_corpus function 
clean_corpus <- function(corpus) {
    corpus <- tm_map(corpus, removePunctuation)
    corpus <- tm_map(corpus, removeNumbers)
    corpus <- tm_map(corpus, content_transformer(tolower))
    corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "library", "librarianship"))
    corpus <- tm_map(corpus, stripWhitespace)
    return(corpus)
}
# Create a text dataset
topics.text <- paste(dataset$topics1, dataset$topics2, dataset$topics3, dataset$topics4, dataset$topics5)
# Create a text corpus
topics.corpus <- topics.text %>%
VectorSource() %>%
VCorpus()
# Clean the created corpus
topics.corpus <- clean_corpus(topics.corpus)
# Create a dendogram
topics.corpus %>%
TermDocumentMatrix() %>%
removeSparseTerms(sparse = 0.985) %>%
as.matrix() %>%
dist() %>%
hclust() %>%
plot()
```

## Kindly indicate your primary work location

-   NCR
-   Region I
-   Region II
-   CAR
-   Region III
-   Region IV
-   Region V
-   Region VI
-   Region VII
-   Region VIII
-   Region IX
-   Region X
-   Region XI
-   Region XII
-   CARAGA
-   ARMM

```{r Location, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(location)) %>%
ggplot(aes(x = location, fill = location)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Location", "n=537") + guides(fill = "none") + theme(axis.text.x = element_text(angle = 90)) + scale_fill_viridis_d()
```

```{r LVM, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(lvm)) %>%
ggplot(aes(x = lvm, fill = lvm)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Location", "n=537") + guides(fill = "none") + theme(axis.text.x = element_text(angle = 90)) + scale_fill_viridis_d()
```

## Question: Have you moved out of your original / permanent residence in order to work on your current work place?

-   Yes
-   No

```{r Work Travel, echo=FALSE}                                    
# Graph the data
dataset %>%
filter(!is.na(worktravel)) %>%
ggplot(aes(x = worktravel, fill = worktravel)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + guides(fill = "none") + ggtitle("Distribution of Responses: Work Travel", "n=565") + scale_fill_viridis_d()
```

## Is Filipino / Tagalog your native language?

-   Yes
-   No

```{r Filipino as First Language, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(filipino)) %>%
ggplot(aes(x = filipino, fill = filipino)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + guides(fill = "none") + ggtitle("Distribution of Responses: Filipino as First Language", "n=550") + scale_fill_viridis_d()
```

## Kindly check the local languages or dialects you can speak on a conversational level other than Filipino / Tagalog

-   Ilocano
-   Cebuano
-   Ilonggo
-   Kapampangan
-   Pangasinense
-   Waray
-   Bicolano
-   Others

```{r Dialect, echo=FALSE}
dataset %>%
filter(!is.na(dialect)) %>%
ggplot(aes(x = dialect, fill = dialect)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + guides(fill = "none") + ggtitle("Distribution of Responses: Dialect", "n=391") + scale_fill_viridis_d()
```

## Kindly indicate any foreign languages or dialects you can speak on a conversational level other than English (if any)

```{r other dialect, echo=FALSE}
# Create a clean_corpus function 
clean_corpus <- function(corpus) {
    corpus <- tm_map(corpus, removePunctuation)
    corpus <- tm_map(corpus, removeNumbers)
    corpus <- tm_map(corpus, content_transformer(tolower))
    corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "none", "can", "kankanaey", "tagalog", "filipino", "english"))
    corpus <- tm_map(corpus, stripWhitespace)
    return(corpus)
}
# Create a text corpus
topics.corpus <- dataset$foreignlang %>%
VectorSource() %>%
VCorpus()
# Clean the created corpus
topics.corpus <- clean_corpus(topics.corpus)
# Create a wordcount
term.frequency <- topics.corpus %>%
TermDocumentMatrix() %>%
as.matrix() %>%
rowSums() %>%
sort( , decreasing=TRUE)
term.frequency[1:10]
```

## Kindly indicate the type of library you are currently working in

```{r Library Type, echo=FALSE}
# Graph the data
dataset %>%
filter(!is.na(type)) %>%
ggplot(aes(x = type, fill = type)) + geom_bar() + geom_text(aes(label = ..count..), stat = "count", vjust = -0.2, colour = "black") + xlab("Distribution of responses") + ylab("Frequency") + guides(fill = "none") + ggtitle("Distribution of Responses: Library Type", "n=473") + scale_fill_viridis_d()
```

## Other than being a librarian, what other roles do you serve in your institution/ organization?

```{r Other roles, echo=FALSE}
# Create a clean_corpus function 
clean_corpus <- function(corpus) {
    corpus <- tm_map(corpus, removePunctuation)
    corpus <- tm_map(corpus, removeNumbers)
    corpus <- tm_map(corpus, content_transformer(tolower))
    corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "library", "librarianship", "none", "librarian"))
    corpus <- tm_map(corpus, stripWhitespace)
    return(corpus)
}
# Create a text corpus
roles.corpus <- dataset$roles %>%
VectorSource() %>%
VCorpus()
# Clean the created corpus
roles.corpus <- clean_corpus(roles.corpus)
# Create a dendogram
roles.corpus %>%
TermDocumentMatrix() %>%
removeSparseTerms(sparse = 0.99) %>%
as.matrix() %>%
dist() %>%
hclust() %>%
plot()
```

## Kindly indicate your current work position

```{r Work position, echo=FALSE}
# Create a clean_corpus function 
clean_corpus <- function(corpus) {
    corpus <- tm_map(corpus, removePunctuation)
    corpus <- tm_map(corpus, removeNumbers)
    corpus <- tm_map(corpus, content_transformer(tolower))
    corpus <- tm_map(corpus, removeWords, c(stopwords("en"),"iii", "library", "librarianship", "none", "librarian", "sole", "librarians"))
    corpus <- tm_map(corpus, stripWhitespace)
    return(corpus)
}
# Create a text corpus
institutionposition.corpus <- dataset$institutionposition %>%
VectorSource() %>%
VCorpus()
# Clean the created corpus
institutionposition.corpus <- clean_corpus(institutionposition.corpus)
# Create a dendogram
institutionposition.corpus %>%
TermDocumentMatrix() %>%
removeSparseTerms(sparse = 0.99) %>%
as.matrix() %>%
dist() %>%
hclust() %>%
plot()
```

## Kindly indicate your primary job / designation inside the library

```{r designation, echo=FALSE, fig.height=6}
# Create a clean_corpus function 
clean_corpus <- function(corpus) {
    corpus <- tm_map(corpus, removePunctuation)
    corpus <- tm_map(corpus, removeNumbers)
    corpus <- tm_map(corpus, content_transformer(tolower))
    corpus <- tm_map(corpus, removeWords, c(stopwords("en"),"iii", "library", "librarianship", "none", "librarian", "sole", "librarians"))
    corpus <- tm_map(corpus, stripWhitespace)
    return(corpus)
}
# Create a text corpus
primaryjob.corpus <- dataset$primaryjob %>%
VectorSource() %>%
VCorpus()
# Clean the created corpus
primaryjob.corpus <- clean_corpus(primaryjob.corpus)
# Create a dendogram
primaryjob.corpus %>%
TermDocumentMatrix() %>%
removeSparseTerms(sparse = 0.99) %>%
as.matrix() %>%
dist() %>%
hclust() %>%
plot()
```

## Kindly indicate your current / existing professional affiliations

```{r affiliation, echo=FALSE}
dataset %>%
summarise("PAARL" = sum(PAARL == TRUE), 
          "PASLI" = sum(PASLI == TRUE), 
          "ASLP" = sum(ASLP == TRUE), 
          "MAHLAP" = sum(MAHLAP == TRUE), 
          "ALAP" = sum(ALAP == TRUE), 
          "ALPS" = sum(ALPS == TRUE), 
          "PGLL" = sum(PGLL == TRUE), 
          "SFA" = sum(SFA == TRUE)) %>%
gather() %>%
ggplot(aes(x = key, y= value, fill = key)) + geom_col(position = "dodge") + xlab("Distribution of responses") + ylab("Frequency") + ggtitle("Distribution of Responses: Materials", "n=195") + guides(fill = "none") + scale_fill_viridis_d() + theme(axis.text.x = element_text(angle = 90)) +
geom_text(x = 1, y = 10, label = "7", colour = "black", size = 4) + 
geom_text(x = 2, y = 9, label = "6", colour = "black", size = 4) + 
geom_text(x = 3, y = 25, label = "23", colour = "black", size = 4) + 
geom_text(x = 4, y = 21, label = "18", colour = "black", size = 4) + 
geom_text(x = 5, y = 131, label = "128", colour = "black", size = 4) + 
geom_text(x = 6, y = 40, label = "37", colour = "black", size = 4) + 
geom_text(x = 7, y = 9, label = "6", colour = "black", size = 4) + 
geom_text(x = 8, y = 14, label = "11", colour = "black", size = 4) 
```

## Kindly indicate what factors influence your decision when it comes to joining a professional organization?

```{r Factor Joining Organizations, echo=FALSE}
# Create a clean_corpus function 
clean_corpus <- function(corpus) {
    corpus <- tm_map(corpus, removePunctuation)
    corpus <- tm_map(corpus, removeNumbers)
    corpus <- tm_map(corpus, content_transformer(tolower))
    corpus <- tm_map(corpus, removeWords, c(stopwords("en")))
    corpus <- tm_map(corpus, stripWhitespace)
    return(corpus)
}
# Create a text corpus
factor.corpus <- dataset$factor %>%
VectorSource() %>%
VCorpus()
# Clean the created corpus
factor.corpus <- clean_corpus(factor.corpus)
# Create a dendogram
factor.corpus %>%
TermDocumentMatrix() %>%
removeSparseTerms(sparse = 0.985) %>%
as.matrix() %>%
dist() %>%
hclust() %>%
plot()
```


